High geomagnetic field intensity recorded by anorthosite xenoliths requires a vigorous late Mesoproterozoic geodynamo

### 2022-02-12 PNAS_manuscript/Supporting Info.tex
Updates from Overleaf

\begin{figure*}[h!]
\noindent\includegraphics[width=17.8 cm]{Cooling_rate_correction.pdf}
\centering
\caption{{Graph of predicted paleointensity overestimate due to slow cooling of the intrusive Beaver River diabase and anorthosite xenoliths relative to the cooling rate in laboratory following the model of \citealp{Halgedahl1980a}. Because the majority of the anorthosites have unblocking temperatures between 500\textdegree C and 580\textdegree C, we estimate that the slow cooling during natural remanence acquisition could have resulted in a 36\% overestimate. Thus, a correction factor of 0.74 is applied at specimen level for the paleointensity summary plot.  }}
\label{fig:PINT_cooling_corrected}
\end{figure*}

@@

% \clearpage

@@

>>>>

\begin{figure*}[h!]
\noindent\includegraphics[width=17.8 cm]{Cooling_rate_correction.pdf}
\centering
\caption{{Graph of predicted paleointensity overestimate due to slow cooling of the intrusive Beaver River diabase and anorthosite xenoliths relative to the cooling rate in laboratory following the model of \citealp{Halgedahl1980a}. Because the majority of the anorthosites have unblocking temperatures between 500\textdegree C and 580\textdegree C, we estimate that the slow cooling during natural remanence acquisition could have resulted in a 36\% overestimate. Thus, a correction factor of 0.74 is applied at specimen level for the paleointensity summary plot.}}
\label{fig:PINT_cooling_corrected}
\end{figure*}

@@

\begin{figure*}[h!]
\noindent\includegraphics[width=0.9\textwidth]{Cenozoic_resample_SI.pdf}
\centering
\caption{\footnotesize{A) Summary plot of individual specimen absolute paleointensity results (square symbols) and their averages and standard deviations at site level (black bars with grey uncertainty boxes) from this study. All results are corrected for cooling rate with a factor of 0.74. Each `AX' site is an individual anorthosite xenolith within the Beaver River diabase. The sites with successful experiments come from 3 regions which would have cooled at distinct times yielding similar estimates within the each region with differences between regions. B) Specimen level means calculated for these regions are compared to the distribution of intensities calculated from the existing paleointensity data in the PINT database (PINT v8.0.0; \url{http://www.pintdb.org/}; \citealp{Bono2021a}) at the latitude corresponding to the paleolatitude of study region (22\textdegree N). C) The mean of the 3 regional means is compared to means calculated from 3 random values drawn from the Cenozoic data. The paleointensity records used for resampling are filtered for Q$_{PI} \geq$3 \cite{Biggin2014a}. The distribution represents a total of 10,000 iterations of taking 3 random draws and calculating the mean.}}
\label{fig:Cenozoic_PINT}
\end{figure*}

@@

\begin{table}[]
\centering
\caption{\footnotesize{Summary paleointensity result statistics at site-level, region-level, and overall arithmetic means. The statistics names are the same as in Table \ref{tab:PINT_result}}. n represents the total number of specimen- or site-level results used for calculating mean values. inc$_{tc}$ is the tilt corrected mean inclination. Site-level means for AX6, AX8, AX10, AX11, AX12, AX13, AX16 are calculated based on specimen results. Regional means for Carlton Peak, Kennedy Creek, and Silver Bay are calculated by grouping specimen results from AX6 and AX8 and AX10, AX11 and AX13, AX12 and AX16, respectively. Overall site mean values are calculated using all site level results in this table. Overall region mean values are calculated using all regional mean results in this table. }
\begin{tabular}{cccccccccc}
Group               & B$_{anc}$ & n  & FRAC & GAP-MAX & MAD ($^\circ$) & DANG ($^\circ$) & inc$_{tc}$ & $\gamma$ & VDM (ZAm$^2$) \\
AX6                 & 30.33     & 3  & 0.69 & 0.13    & 3.55           & 2.66            & 38.9       & 2.63     & 48.76         \\
AX8                 & 52.4      & 3  & 0.66 & 0.17    & 4.28           & 2.15            & 40.3       & 7.3      & 83.14         \\
AX10                & 46.82     & 3  & 0.7  & 0.23    & 4.98           & 2.14            & 36.6       & 6.1      & 76.81         \\
AX12                & 38.1      & 6  & 0.75 & 0.22    & 3.26           & 2.53            & 55.2       & 5.98     & 51.31         \\
AX16                & 44.15     & 11 & 0.68 & 0.19    & 4.19           & 1.96            & 49.2       & 3.97     & 63.87         \\
AX11                & 73.34     & 7  & 0.68 & 0.19    & 3.85           & 1.82            & 35.2       & 6.63     & 121.73        \\
AX13                & 76.63     & 7  & 0.73 & 0.2     & 5.7            & 1.67            & 35.1       & 5        & 127.29        \\
Carlton Peak        & 43.18     & 9  & 0.68 & 0.17    & 4.27           & 2.32            & 38.6       & 5.34     & 69.57         \\
Kennedy Creek       & 74.98     & 14 & 0.7  & 0.2     & 4.78           & 1.74            & 35.15      & 5.81     & 124.51        \\
Silver Bay          & 42.02     & 17 & 0.71 & 0.2     & 3.86           & 2.16            & 51.32      & 4.68     & 59.43         \\
overall site mean   & 51.68     &    &      &         &                &                 &            &          & 81.84         \\
overall region mean & 53.39     &    &      &         &                &                 &            &          & 84.5         
\end{tabular}
\end{table}
